---
title: "Fall 2024 VIE PreAssignment"
author: "YOURNAME"
date: "DATE"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pre-class Assignment: Introduction to R for Business Analytics

## Setup

I assume you can install R and R-Studio.  Further, as a new R programmer you will need to use the following commands one time to install libraries used in this pre-assignment.

`install.pakages('some library name')`

## Objective

The aim of this pre-assignment is help you catch up to others in the cohort that attended the Harvard session.  This is meant to help you familiarize yourself with R. Your learning objectives include:

1. Loading data into R 
2. Perform basic exploratory data analysis (EDA).
3. Create visualizations using ggplot2 (and I also like ggthemes).
4. Fit a basic linear regression model and interpret its output.  My expectation is that you understand a linear regression as its from statistics and shouldn't be complicated.  Remember you can always look up on an LLM, stackoverflow or google search.
5. Examine the model and identify some relevant KPIs.

## Data

We'll use a dataset from Kaggle called [Superstore Sales](https://www.kaggle.com/jr2ngb/superstore-data). 
This dataset includes ~52k rows and several useful columns for our analysis, including:

- "Row.ID"         
- "Order.ID"  
- "Order.Date"     
- "Ship.Date"
- "Ship.Mode"     
- "Customer.ID" 
- "Customer.Name" 
- "Segment"
- "City"  
- "State"         
- "Country"
- "Postal.Code"    
- "Market"   
- "Region" 
- "Product.ID"    
- "Category" 
- "Sub.Category"
- "Product.Name"
- "Sales"
- "Quantity"      
- "Discount" 
- "Profit" 
- "Shipping.Cost"
- "Order.Priority"

The data containts product sales & profits making it realistic and business-related.

## Instructions

### Step 1: Load the Data

You'll be loading data from a CSV file into R which requires the `read.csv` function.  The URL is to our class repository but you could also change it to a local path too.

```{r data, include=T}
# Load Data, create an object called SuperstoreData with the correct table reading function
_________ <- ____.___("https://github.com/kwartler/Vienna_24/raw/refs/heads/main/Fall_2024/preAssignment/advanced/superstore_dataset2011-2015.csv")
```

### Step 2: Explore the Data

Use the `str()`, `class()` and `summary()` functions to understand the data.  Find the function that let's you *examine the top 6 rows by default and put it in this section*.

```{r EDA, include=T}
# Check the structure of data
___(___)

# What class is this object?
___(___)

# Obtain summary statistics 
____(___)

# Examine the top 6 rows using a function
___(___)
```

### Step 3: Visualization

Your business audience will be able to understand a lot of patterns with compelling visuals.  Build a scatter plot using `ggplot` so x is "Discount" and y is "Profit".  Also, find the function to `correlate both of these variables and put it in this code chunk`.  You can also use `ggthemes` to add a theme layer so its more appealing.

```{r viz, include=T}
# Load the ggplot2 & ggthemes library
library(___)
library(___)

# Scatter plot of Discount vs. Profit
# add a ggtitle() with  "Scatterplot of Discount vs Profit"
# Make the visual have a google theme from ggthemes
# make the points darkred
ggplot(data = ___, aes(x = ___, y = __)) +
  geom_point(color = '___') +
  ggtitle("___") +
  ____()

# What is the correlation between Discount & Profit?
___(____$___, ___$___)
```

### Step 4: Fit a Regression Model

Now, we'll use a linear regression model to test if "Discount", "Quantity", & "Shipping.Cost" can predict the "Profit". You will need to setup a formula in this format:

`y ~ variable1 + variable2 + variable3`

```{r fit, include=T}
# Fit a simple linear regression model, call the model object `fit`
# Look up the function name for a linear model
___ <- __(y ~ variable1 + variable2 + variable3, data = ___)

# Print model `summary()`
___(___)

# Fit ANOTHER  linear regression model, call the model object `fit2`
# Add + 0 onto the variable formula used previously
___ <- __(____, data = ___)

# Print model `summary()`
___(___)

```

### Step 5: Assess the Models

Interpret the model results. Examine the models' coefficients, adjusted R-squared &  p-values. 

Some questions to consider:

- How well does the model explain the variation?
- Are the model's predictors significant? 

Write your observations below.

## Deliverable

Submit your well-structured, thoroughly-commented R markdown script including outputs. Also, provide your interpretation and insights obtained from the regression models in the HTML when knitting.